simodels: A package for Spatial Interaction Modelling

### 2024-07-26 paper/paper.qmd
[](.pkg) syntax

---
title: "simodels: A package for Spatial Interaction Modelling"
format:
    jss-pdf:
        keep-tex: true
    jss-html: default
# author:
#   - name: Achim Zeileis
#     affiliations:
#       - name: Universität Innsbruck
#         department: Department of Statistics
#         address: Universitätsstr. 15
#         city: Innsbruck
#         country: Austria
#         postal-code: 6020
#       - Journal of Statistical Software
#     orcid: 0000-0003-0918-3766
#     email: Achim.Zeileis@R-project.org
#     url: https://www.zeileis.org/
#   - name: Second  Author
#     affiliations:
#       - Plus Affiliation
# abstract: |
#   This short article illustrates how to write a manuscript for the
#   _Journal of Statistical Software_ (JSS) using its {{< latex >}} style files.
#   Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
#   it is recommended to keep the {{< latex >}} code as simple as possible,
#   i.e., avoid inclusion of packages/commands that are not necessary.
#   For outlining the typical structure of a JSS article some brief text snippets are employed that have been inspired by @ZeileisKleiberJackman2008, discussing count data regression in [R]{.proglang}. Editorial comments and instructions are marked by vertical bars.
abstract: |
  This article introduces the `simodels` package for spatial interaction modelling in R. The package provides functions for estimating spatial interaction models, including unconstrained gravity models and models that are production-, attraction-, or doubly-constrained.

@@

Before describing the functions in the package, it's worth implementing SIMs from first principles, to gain an understanding of how they work.
The code presented below was written before the functions in the [simodels]{.pkg} package were developed, building on @dennett_modelling_2018.
The aim is to demonstrate a common way of running SIMs, in a for loop, rather than using vectorised operations used in `simodels`.

>>>>

---
title: "simodels: A package for Spatial Interaction Modelling"
format:
    jss-pdf:
        keep-tex: true
    jss-html: default
# author:
#   - name: Achim Zeileis
#     affiliations:
#       - name: Universität Innsbruck
#         department: Department of Statistics
#         address: Universitätsstr. 15
#         city: Innsbruck
#         country: Austria
#         postal-code: 6020
#       - Journal of Statistical Software
#     orcid: 0000-0003-0918-3766
#     email: Achim.Zeileis@R-project.org
#     url: https://www.zeileis.org/
#   - name: Second  Author
#     affiliations:
#       - Plus Affiliation
# abstract: |
#   This short article illustrates how to write a manuscript for the
#   _Journal of Statistical Software_ (JSS) using its {{< latex >}} style files.
#   Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
#   it is recommended to keep the {{< latex >}} code as simple as possible,
#   i.e., avoid inclusion of packages/commands that are not necessary.
#   For outlining the typical structure of a JSS article some brief text snippets are employed that have been inspired by @ZeileisKleiberJackman2008, discussing count data regression in [R]{.proglang}. Editorial comments and instructions are marked by vertical bars.
abstract: |
  This article introduces the [simodels]{.pkg} package for spatial interaction modelling in R. The package provides functions for estimating spatial interaction models, including unconstrained gravity models and models that are production-, attraction-, or doubly-constrained.

@@

Before describing the functions in the package, it's worth implementing SIMs from first principles, to gain an understanding of how they work.
The code presented below was written before the functions in the [simodels]{.pkg} package were developed, building on @dennett_modelling_2018.
The aim is to demonstrate a common way of running SIMs, in a for loop, rather than using vectorised operations used in [simodels]{.pkg}.
